Covariate Analysis of ROSMAP Reprocessed counts

### 2020-12-16 code/2020_12_09_ROSMAP_FullCohort_Regress_hg38.Rmd
recommit

@@

#assign gne names to a variable to iterate over
temp<-colnames(EXP)

#BRAAK
Path <- 'braaksc'
mark<-Sys.time()
BRAAK_ACC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'ACC' )
Sys.time() - mark

mark<-Sys.time()
BRAAK_PCC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'PCC' )
Sys.time() - mark

mark<-Sys.time()
BRAAK_DLPFC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'DLPFC' )
Sys.time() - mark

BRAAK <- rbind( BRAAK_ACC, BRAAK_PCC, BRAAK_DLPFC )

#CERAD
Path <- 'ceradsc'
mark<-Sys.time()
CERAD_ACC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'ACC' )
Sys.time() - mark
mark<-Sys.time()
CERAD_PCC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'PCC' )
Sys.time() - mark
mark<-Sys.time()
CERAD_DLPFC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'DLPFC' )
Sys.time() - mark

CERAD <- rbind( CERAD_ACC, CERAD_PCC, CERAD_DLPFC )

#COGDX
Path <- 'cogdx'
mark<-Sys.time()
cogdx_ACC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'ACC' )
Sys.time() - mark
mark<-Sys.time()
cogdx_PCC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'PCC' )
Sys.time() - mark
mark<-Sys.time()
cogdx_DLPFC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'DLPFC' )
Sys.time() - mark

@@

#DCFDX_LV
Path <- 'dcfdx_lv'
mark<-Sys.time()
dcfdx_ACC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'ACC' ) 
Sys.time() - mark
mark<-Sys.time()
dcfdx_PCC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'PCC' ) 
Sys.time() - mark
mark<-Sys.time()
dcfdx_DLPFC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'DLPFC' ) 
Sys.time() - mark

@@

```{r NeuroPath_Finish, include=FALSE, cache=TRUE}
####--Pick Up Here--###

My.P.Adj <- function (p, method = p.adjust.methods, n = length(p)){
    method <- match.arg(method)
    if (method == "fdr") 
        method <- "BH"
    nm <- names(p)
    p <- as.numeric(p)
    p0 <- setNames(p, nm)
    if (all(nna <- !is.na(p))) 
        nna <- TRUE
    p <- p[nna]
    lp <- length(p)
    #stopifnot(n >= lp)
    if (n <= 1) 
        return(p0)
    if (n == 2 && method == "hommel") 
        method <- "hochberg"
    p0[nna] <- switch(method, bonferroni = pmin(1, n * p), holm = {
        i <- seq_len(lp)
        o <- order(p)
        ro <- order(o)
        pmin(1, cummax((n + 1L - i) * p[o]))[ro]
    }, hommel = {
        if (n > lp) p <- c(p, rep.int(1, n - lp))
        i <- seq_len(n)
        o <- order(p)
        p <- p[o]
        ro <- order(o)
        q <- pa <- rep.int(min(n * p/i), n)
        for (j in (n - 1L):2L) {
            ij <- seq_len(n - j + 1L)
            i2 <- (n - j + 2L):n
            q1 <- min(j * p[i2]/(2L:j))
            q[ij] <- pmin(j * p[ij], q1)
            q[i2] <- q[n - j + 1L]
            pa <- pmax(pa, q)
        }
        pmax(pa, p)[if (lp < n) ro[1L:lp] else ro]
    }, hochberg = {
        i <- lp:1L
        o <- order(p, decreasing = TRUE)
        ro <- order(o)
        pmin(1, cummin((n + 1L - i) * p[o]))[ro]
    }, BH = {
        i <- lp:1L
        o <- order(p, decreasing = TRUE)
        ro <- order(o)
        pmin(1, cummin(n/i * p[o]))[ro]
    }, BY = {
        i <- lp:1L
        o <- order(p, decreasing = TRUE)
        ro <- order(o)
        q <- sum(1/(1L:n))
        pmin(1, cummin(q * n/i * p[o]))[ro]
    }, none = p)
    p0
}

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
#parentId = 'syn21277617';
activityName = 'Covariate Regression';
activityDescription = 'Covariate analysis and Regression of aligned effective counts with GRCh38 with CQN normalisation (DLPFC)';
thisFileName <- '2020_12_09_ROSMAP_FullCohort_Regress_hg38.Rmd'
# Github link
thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
```

@@

CODE <- syn_temp$store(synapseclient$Folder(name = folderName, parentId = parentId))

@@

# Store filtered counts
PROCESSED_COUNTS$filteredExprMatrix$counts %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_Regressed_Counts.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_Counts.tsv', name = 'Counts (filtered raw)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'filteredCounts'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store Estimated counts
NEW.COUNTS %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_Regressed_eCounts.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_Counts.tsv', name = 'Counts (estimated)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'estimatedCounts'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store logCPM
CQN.GENE_EXPRESSION$y %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_Regressed_logCPM.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'filteredLCPM'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store cqn offsets
CQN.GENE_EXPRESSION$offset %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_Regressed_offset.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_offset.tsv', name = 'Gene length and GC content offset', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'offset'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store design matrix
MODEL1 %>%
  rownameToFirstColumn('SampleID') %>%
  write.table(file = 'ROSMAP_DLPFC_Regressed_Design.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_Design.tsv', name = 'Design Matrix', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'designMatrix'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store surrogate variables
SURR.VAR %>%
  rownameToFirstColumn('SampleID') %>%
  write.table(file = 'ROSMAP_DLPFC_Regressed_SurVar.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_SurVar.tsv', name = 'Surrogate Variables', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'surrogateVariables'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store residual gene expression for network analysis
RESIDUAL.NET.GENE_EXPRESSION %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_netResidualExpression.tsv', name = 'Normalised, and covariates removed residual expression (for network analysis)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'residualGeneExpForNetAnlz'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store differential expression results
rbindlist(all.diff.exp, use.names = T, fill = T, idcol = 'Model') %>%
  write.table(file = 'ROSMAP_DLPFC_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_DiffExpression.tsv', name = 'Differential Expression Results (cogdx)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'Diff_Exp'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

>>>>

#Filter for Rin Here#

@@

#assign gne names to a variable to iterate over
temp<-colnames(EXP)
```
```{r NeuroPath_Associtation_1_1, include=FALSE, cache=TRUE}
#BRAAK
Path <- 'braaksc'
mark<-Sys.time()
BRAAK_ACC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'ACC' )}, error=function(e) NULL)
Sys.time() - mark
```
```{r NeuroPath_Associtation_1_2, include=FALSE, cache=TRUE}
mark<-Sys.time()
BRAAK_PCC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'PCC' )}, error=function(e) NULL)
Sys.time() - mark
```

```{r NeuroPath_Associtation_1_3, include=FALSE, cache=TRUE}
mark<-Sys.time()
BRAAK_DLPFC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'DLPFC' )}, error=function(e) NULL)
Sys.time() - mark

BRAAK <- rbind( BRAAK_ACC, BRAAK_PCC, BRAAK_DLPFC )
```
```{r NeuroPath_Associtation_2_1, include=FALSE, cache=TRUE}
#CERAD
Path <- 'ceradsc'
mark<-Sys.time()
CERAD_ACC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'ACC' )}, error=function(e) NULL)
Sys.time() - mark
```
```{r NeuroPath_Associtation_2_2, include=FALSE, cache=TRUE}
mark<-Sys.time()
CERAD_PCC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'PCC' )}, error=function(e) NULL)
Sys.time() - mark
```
```{r NeuroPath_Associtation_2_3, include=FALSE, cache=TRUE}

mark<-Sys.time()
CERAD_DLPFC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'DLPFC' )}, error=function(e) NULL)
Sys.time() - mark

CERAD <- rbind( CERAD_ACC, CERAD_PCC, CERAD_DLPFC )
```
```{r NeuroPath_Associtation_3_1, include=FALSE, cache=TRUE}

#COGDX
Path <- 'cogdx'
mark<-Sys.time()
cogdx_ACC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'ACC' )}, error=function(e) NULL)
Sys.time() - mark
```
```{r NeuroPath_Associtation_3_2, include=FALSE, cache=TRUE}

mark<-Sys.time()
cogdx_PCC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'PCC' )}, error=function(e) NULL)
Sys.time() - mark
```
```{r NeuroPath_Associtation_3_3, include=FALSE, cache=TRUE}

mark<-Sys.time()
cogdx_DLPFC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'DLPFC' )}, error=function(e) NULL)
Sys.time() - mark
```

```{r NeuroPath_Associtation_4_1, include=FALSE, cache=TRUE}

@@

#DCFDX_LV
Path <- 'dcfdx_lv'
mark<-Sys.time()
dcfdx_ACC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'ACC' ) }, error=function(e) NULL)
Sys.time() - mark
```
```{r NeuroPath_Associtation_4_2, include=FALSE, cache=TRUE}

mark<-Sys.time()
dcfdx_PCC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'PCC' ) }, error=function(e) NULL)
Sys.time() - mark
```
```{r NeuroPath_Associtation_4_3, include=FALSE, cache=TRUE}
mark<-Sys.time()
dcfdx_DLPFC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'DLPFC' ) }, error=function(e) NULL)
Sys.time() - mark

@@

```{r NeuroPath_Finish, include=FALSE, cache=TRUE}

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = '"syn23640229"';
activityName = 'Covariate Regression';
activityDescription = 'Covariate analysis and Regression of aligned effective counts with GRCh38 with CQN normalisation (DLPFC)';
thisFileName <- '2020_12_09_ROSMAP_FullCohort_Regress_hg38.Rmd'
# Github link
thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
```

@@

CODE <- syn_temp$store(synapseclient$Folder(name = "Full_RosMap_OldCode", parentId = "syn23640229"))

@@

# Store filtered counts
PROCESSED_COUNTS$filteredExprMatrix$counts %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_Regressed_Counts.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Regressed_Counts.tsv', name = 'Counts (filtered raw)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'filteredCounts'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store Estimated counts
NEW.COUNTS %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_Regressed_eCounts.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Regressed_eCounts.tsv', name = 'Counts (estimated)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'estimatedCounts'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store logCPM
CQN.GENE_EXPRESSION$y %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_Regressed_logCPM.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Regressed_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'filteredLCPM'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store cqn offsets
CQN.GENE_EXPRESSION$offset %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_Regressed_offset.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Regressed_offset.tsv', name = 'Gene length and GC content offset', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'offset'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store design matrix
MODEL1 %>%
  rownameToFirstColumn('SampleID') %>%
  write.table(file = 'ROSMAP_Regressed_Design.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Regressed_Design.tsv', name = 'Design Matrix', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'designMatrix'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store surrogate variables
SURR.VAR %>%
  rownameToFirstColumn('SampleID') %>%
  write.table(file = 'ROSMAP_Regressed_SurVar.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Regressed_SurVar.tsv', name = 'Surrogate Variables', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'surrogateVariables'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store residual gene expression for network analysis
RESIDUAL.NET.GENE_EXPRESSION %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Regressed_netResidualExpression.tsv', name = 'Normalised, and covariates removed residual expression (for network analysis)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'residualGeneExpForNetAnlz'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store differential expression results
rbindlist(all.diff.exp, use.names = T, fill = T, idcol = 'Model') %>%
  write.table(file = 'ROSMAP_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DiffExpression.tsv', name = 'Differential Expression Results (cogdx)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'Diff_Exp'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
